Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/appendix.Rmd
add reference to activity x location graph and names in appendix, rmd

```{r, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

>>>>

```{r activities_by_lo, fig.width=6.5, fig.height=3.0, fig.cap="Counts of activities by location, including multilocation videos."}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add reference to activity x location graph and names in appendix, rmd

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.

@@

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

>>>>

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%c
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. However, every location was of course associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.

@@

Second, we also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work and to exclude the portion of the frame most likely to contain children's own hands.
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.
